Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-04-05 WSSSPE1_report/WSSSPE1_summary_report.tex
Includes rOpenSci example.

In practice, there are example for both extremes of the spectrum. For
example, in the life sciences the iPlant Collaborative~\cite{iPlant},
the Galaxy Project~\cite{Galaxy}, and Qiime~\cite{Qiime} are large
multi-year projects with significant software infrastructure funding
and deliverables. Typically though these are the exception rather than
the rule, and particularly in the long tail of science the
scientist-developer predominates. For providing these with better
training in software engineering best practices, initiatives such as
Software Carpentry~\cite{SoftwareCarpentry} have been especially
valuable, and Software Carpentry also shown how such training could
scale.

>>>>

In practice, there are example for both extremes of the spectrum. For
example, in the life sciences the iPlant Collaborative~\cite{iPlant},
the Galaxy Project~\cite{Galaxy}, and Qiime~\cite{Qiime} are large
multi-year projects with significant software infrastructure funding
and deliverables. Typically though these are the exception rather than
the rule, and particularly in the long tail of science the
scientist-developer predominates, even for software that is widely
used or crosses domain boundaries such as
rOpenSci~\cite{rOpenSci}. For better training domain scientists at
least in basic software engineering best practices, initiatives such
as Software Carpentry~\cite{SoftwareCarpentry} have demonstrated how
this could be achieved at scale.
